Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

This motivates the following interlacing connection structure between
levels. For each level in the info-graph, there are $\NG^2$ groups for
some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,\ldots,L\}$
and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
visualization of simple case with $\NG = 2$). Two observations are
in order:
% \OMIT{(i) The number of groups does not grow with $L$ and stays as
%   $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
%   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
\begin{description}

\item(i) For any level $l \geq 2$, fix the last group index to be $v$,
  and consider the set of groups
  $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
  and $G_{l-1,2,1}$ circled in the Figure
  \ref{fig:llevel-connecting}). The agents in this set of groups
  observe the same sub-history. They get ``lucky'' for some arm at the
  same time.
\item(ii) For each set of groups in level $l-1$, agents in level $l$ see
the history of agents in one of these groups. Therefore, for each arm
$a$, we just need one set of groups in level $l-1$ to get ``lucky''
and then all agents in level $l$ will see enough pulls of arm $a$.
\end{description}
\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}

@@

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}
\xhdr{Additional groups for boundary cases.} Recall in our 3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm. The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level. We need to worry about the situation in which the sub-optimal arm does not get pulled enough times in the first two levels and some agents in the third level may pull the sub-optimal arm. Such situation is naturally ruled out in our 3-level policy for the following reason. Agents in the third level observe the history of the entire first level while agents in the second level only observes the history of a single first-level group. For each arm, even if it is not explored enough times in the second level, its empirical mean concentrates closer to its actual mean in the history observed by a third-level agent than the one observed by a second-level agent. Therefore, although the gap in the medium gap case is just not large enough for agents in the second level to all pull the best arm, it is large enough for agents in the third level to all pull the best arm.

>>>>

This motivates the following interlacing connection structure between
levels. For each level in the info-graph, there are $\NG^2$ groups for
some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,\ldots,L\}$
and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
visualization of simple case with $\NG = 2$). Two observations are
in order:
% \OMIT{(i) The number of groups does not grow with $L$ and stays as
%   $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
%   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
\begin{itemize}
\item[(i)] Consider level $(l - 1)$ and fix the last group index to be
  $v$, and consider the set of groups
  $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
  and $G_{l-1,2,1}$ circled in the Figure
  \ref{fig:llevel-connecting}). The agents in any group of
  $\cG_{l-1, v}$ observe the same sub-history. If the empirical mean
  of arm $a$ is sufficiently high in their shared sub-history, then all groups in $\cG_{l-1, v}$ will become ``lucky'' groups for $a$.

\item[(ii)] Every agent in level $l$ observes the sub-history from
  $\NG$ $(l-1)$-th level groups, each of which belonging to a
  different set $\cG_{l-1, v}$. Thus, for each arm $a$, we just need
  one set of groups $\cG_{l-1, v}$ in level $l-1$ to be ``lucky'' for
  $a$ and then all agents in level $l$ will see sufficient arm $a$
  pulls.
 \OMIT{For each set of groups
    in level $l-1$, agents in level $l$ see the history of agents in
    one of these groups. Therefore, for each arm $a$, we just need one
    set of groups in level $l-1$ to get ``lucky'' and then all agents
    in level $l$ will see enough pulls of arm $a$.}
\end{itemize}

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \foreach \x in {0,3,6,9}
 {
 \filldraw[fill=purple!20!white]
 (\x+0,7.5)--(\x+2,7.5)--(\x+2,8.5)--(\x+0,8.5)--cycle;
 \filldraw[fill=green!20!white]
 (\x+0,5)--(\x+2,5)--(\x+2,6)--(\x+0,6)--cycle;
 \filldraw[fill=blue!20!white]
 (\x+0,2.5)--(\x+2,2.5)--(\x+2,3.5)--(\x+0,3.5)--cycle;
 }
\foreach \y in {2.5,5,7.5}
{
  \node at (12.5,\y+0.5){$\cdots$};
}

@@

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}

\paragraph{Amplifying groups for boundary cases.} Recall in our
3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the
boundary case when the gap $|\mu_1-\mu_2|$ is
$\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and
$O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is
not large enough to conclude that with high probability agents in both
the second level and the third level all pull the best arm. The gap is
also not small enough to conclude that with high probability both arms
are explored enough times in the second level. We need to worry about
the situation in which the sub-optimal arm does not get pulled enough
times in the first two levels and some agents in the third level may
pull the sub-optimal arm. Such situation is naturally ruled out in our
3-level policy for the following reason. Agents in the third level
observe the history of the entire first level while agents in the
second level only observes the history of a single first-level
group. For each arm, even if it is not explored enough times in the
second level, its empirical mean concentrates closer to its actual
mean in the history observed by a third-level agent than the one
observed by a second-level agent. Therefore, although the gap in the
medium gap case is just not large enough for agents in the second
level to all pull the best arm, it is large enough for agents in the
third level to all pull the best arm.
